Title Goes Here

### 2017-08-16 analysis/paper/paper.Rmd
add data and code

```{r demo, eval = FALSE}
1 + 1
```

>>>>

```{r demo, eval = FALSE}
# install.packages("rdatacite")

library(rdatacite)
# dc_arch <- dc_search(q = "archaeology", rows = pretty(100000)[2])
# saveRDS(dc_arch, "dc_arch.rds")
dc_arch <- readRDS("dc_arch.rds")

library(tidyverse)
library(stringr)
glimpse(dc_arch)

dc_arch <- 
dc_arch %>% 
mutate(the_text =  toupper(gsub(" |_|\\(|\\)", "-", rights)),
       the_text = gsub("(\\-)\\1+", "\\1", the_text),
       the_text = gsub("-$", "", the_text)) %>% 
  mutate(cc = case_when(
    grepl("SEMANTICS/OPENACCESS", the_text) ~ "EU Open Access",
    grepl("SEMANTICS/RESTRICTEDACCESS", the_text) ~ "EU Restricted Access",
    grepl("SEMANTICS/CLOSEDACCESS", the_text) ~ "EU Closed Access",
    grepl("CC-BY-[^NC-ND]|CC-BY$|ATTRIBUTION-LICENSE|ATTRIBUTION-[^NON]", the_text) ~ "CC-BY",
    grepl("CC-BY-NC-[^ND]|BY-NC-[^ND]|CC-NC$|ATTRIBUTION-NON-COMMERCIAL-", the_text) ~ "CC-BY-NC",
    grepl("CC-BY-NC-SA-[^ND]|CC-NC-SA$|ATTRIBUTION-NON-COMMERCIAL-SHARE", the_text) ~ "CC-BY-NC-SA",
    grepl("CC-BY-NC-ND|BY-NC-ND|ATTRIBUTION-NONCOMMERCIAL-NO-DERIVATIVE|ATTRIBUTION-NONCOMMERCIAL-NODERIVATIVES|ATTRIBUTION-NONCOMMERCIAL-NODERIVS|NAMENSNENNUNG-NICHTKOMMERZIELL-KEINEBEARBEITUNG|NAMENSNENNUNG-KEINE-KOMMERZIELLE-NUTZUNG", the_text) ~ "CC-BY-NC-ND",
    grepl("ADS|ARCHAEOLOGYDATASERVICE", the_text) ~ "ADS",
    grepl("CC0|CC-0|ZERO", the_text) ~ "CC-0"
  )) %>% 
  mutate(yyyy_created =  as.numeric(substr(created, 1,4)),
         yyyy_date =  as.numeric(substr(date, 1,4)))

# variables of interest:
# datacentre
# allocator 
# date
# creator
# description
# langauge
# contributor
# rights
# publisher

# select cols of interest
xx <- 
dc_arch %>% 
  select( datacentre,
          allocator ,
          date,
          creator,
          description,
          language,
          contributor,
          rights,
          publisher)

# make a list of tallys of each col
# yy <- map(xx, ~.x %>% as_data_frame() %>% group_by(value) %>% tally())

# output <- vector("list", ncol(xx))
# for(i in seq_len(ncol(xx))){
#   output[[i]] <- 
#     arrange(as_data_frame(table(xx[ , i])), desc(n))
#   gc()
#   print(i)
# }

datacentre<-  arrange(as_data_frame(table(xx[ , "datacentre"])), desc(n))
allocator <-  arrange(as_data_frame(table(xx[ , "allocator"])), desc(n))
dates<-        arrange(as_data_frame(table(xx[ , "date"])), desc(n))
creator<-     arrange(as_data_frame(table(xx[ , "creator"])), desc(n)) 
# description<- arrange(as_data_frame(table(xx[ , "description"])), desc(n)) 
language<-    arrange(as_data_frame(table(xx[ , "language"])), desc(n))  
contributor<- arrange(as_data_frame(table(xx[ , "contributor"])), desc(n)) 
rights<-      arrange(as_data_frame(table(xx[ , "rights"])), desc(n)) 
publisher <-  arrange(as_data_frame(table(xx[ , "publisher"])), desc(n))

# clean up rights a bit

theme_new <- function(base_size = 12){
  theme_bw(base_size = base_size) %+replace%
    theme(
      #axis.title.x=element_blank(),
      # axis.title.y=element_blank(),
      axis.title = element_text(size = 14),
      legend.key=element_rect(colour=NA, fill =NA),
      # panel.grid = element_blank(),   
      panel.border = element_rect(fill = NA, colour = "black", size=0.5),
      panel.background = element_rect(fill = "white", colour = "black"), 
      strip.background = element_rect(fill = NA)
    )
}

datacentre_plot <- 
  datacentre %>% 
  mutate(Var1 = str_wrap(Var1, 20)) %>% 
  slice(1:10) %>% 
ggplot(aes(reorder(Var1, n),
           n)) +
  geom_col() +
  coord_flip() +
  xlab("Data centre") +
  ylab("") +
  theme_new() +
  theme(axis.text.y  = element_text(size = 8))

allocator_plot <- 
ggplot(allocator[1:10,],
       aes(reorder(Var1, n),
           n)) +
  geom_col() +
  coord_flip() +
  theme_new()

creator_plot <- 
ggplot(creator[1:30,],
       aes(reorder(Var1, n),
           n)) +
  geom_col() +
  coord_flip() +
  theme_new()

language_plot <- 
  language %>% 
  mutate(Var2 = ifelse(grepl("en|En", Var1), "en", Var1)) %>% 
  mutate(Var2 = ifelse(grepl("de|ger", Var2), "de", Var2)) %>% 
  group_by(Var2) %>% 
  tally(sort = TRUE) %>% 
  slice(1:5) %>% 
ggplot(aes(reorder(Var2, nn),
           nn)) +
  geom_col() +
  coord_flip()  +
  theme_new() +
  xlab("Language") +
  ylab("")

contributor_plot <- 
ggplot(contributor[1:20,],
       aes(reorder(Var1, n),
           n)) +
  geom_col() +
  coord_flip()  +
  theme_new()

rights_summary <- 
  rights %>% 
  mutate(the_text =  toupper(gsub(" |_|\\(|\\)", "-", Var1)),
         the_text = gsub("(\\-)\\1+", "\\1", the_text),
         the_text = gsub("-$", "", the_text)) %>% 
  mutate(cc = case_when(
    grepl("SEMANTICS/OPENACCESS", the_text) ~ "EU Open Access",
    grepl("SEMANTICS/RESTRICTEDACCESS", the_text) ~ "EU Restricted Access",
    grepl("SEMANTICS/CLOSEDACCESS", the_text) ~ "EU Closed Access",
    grepl("CC-BY-[^NC-ND]|CC-BY$|ATTRIBUTION-LICENSE|ATTRIBUTION-[^NON]", the_text) ~ "CC-BY",
    grepl("CC-BY-NC-[^ND]|BY-NC-[^ND]|CC-NC$|ATTRIBUTION-NON-COMMERCIAL-", the_text) ~ "CC-BY-NC",
    grepl("CC-BY-NC-SA-[^ND]|CC-NC-SA$|ATTRIBUTION-NON-COMMERCIAL-SHARE", the_text) ~ "CC-BY-NC-SA",
    grepl("CC-BY-NC-ND|BY-NC-ND|ATTRIBUTION-NONCOMMERCIAL-NO-DERIVATIVE|ATTRIBUTION-NONCOMMERCIAL-NODERIVATIVES|ATTRIBUTION-NONCOMMERCIAL-NODERIVS|NAMENSNENNUNG-NICHTKOMMERZIELL-KEINEBEARBEITUNG|NAMENSNENNUNG-KEINE-KOMMERZIELLE-NUTZUNG", the_text) ~ "CC-BY-NC-ND",
    grepl("ADS|ARCHAEOLOGYDATASERVICE", the_text) ~ "ADS",
    grepl("CC0|CC-0|ZERO", the_text) ~ "CC-0"
  )) %>% 
  select(cc, n) %>% 
  filter(!is.na(cc)) %>% 
  group_by(cc) %>% 
  tally(sort = TRUE)

rights_plot <- 
ggplot(rights_summary,
       aes(reorder(cc, nn),
           nn)) +
  geom_col() +
  coord_flip()  +
  theme_new() +
  xlab("License") +
  ylab("")

publisher_plot <- 
ggplot(publisher[1:10,],
       aes(reorder(Var1, n),
           n)) +
  geom_col() +
  coord_flip() +
  theme_new()

date_plot <- 
  dates %>% 
  mutate(yyyy = as.numeric(substr(Var1, 1,4))) %>% 
  select(yyyy) %>% 
  ggplot(aes(yyyy)) +
  geom_histogram() +
  theme_new() +
  xlim(c(1950,2017)) +
  xlab("Year") +
  ylab("")

library(plotly)
ggplotly(date_plot)

# why so many in 2010? http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0078080 it's the Dutch

what_2010 <- 
  xx %>% 
  filter(as.numeric(substr(date, 1,4)) == 2010)

why_2013 <- 
  xx %>% 
  filter(as.numeric(substr(date, 1,4)) == 2013) %>% 
  group_by(publisher) %>% 
  tally(sort = TRUE)

why_2012 <- 
  xx %>% 
  filter(as.numeric(substr(date, 1,4)) == 2012) %>% 
  group_by(publisher) %>% 
  tally(sort = TRUE)

why_2011 <- 
  xx %>% 
  filter(as.numeric(substr(date, 1,4)) == 2011) %>% 
  group_by(publisher) %>% 
  tally(sort = TRUE)

why_2010 <- 
xx %>% 
  filter(as.numeric(substr(date, 1,4)) == 2010) %>% 
  group_by(publisher) %>% 
  tally(sort = TRUE)

why_2009 <- 
  xx %>% 
  filter(as.numeric(substr(date, 1,4)) == 2009) %>% 
  group_by(publisher) %>% 
  tally(sort = TRUE)

why_2008 <- 
  xx %>% 
  filter(as.numeric(substr(date, 1,4)) == 2008) %>% 
  group_by(publisher) %>% 
  tally(sort = TRUE)

# panel of plots
# combine plots for lang and data center
datacentre_and_langugage_plot <- 
  datacentre_plot + annotation_custom(ggplotGrob(language_plot),
                                      xmin = 1.15, 
                                      xmax = 6.15,
                                      ymin = 10000,
                                      ymax = 40000
  )

# combine plots for lisc and year
rights_and_date_plot <- 
  rights_plot + annotation_custom(ggplotGrob(date_plot),
                                      xmin = 1, 
                                      xmax = 5,
                                      ymin = 10000,
                                      ymax = 40000
  )

library(gridExtra)
lay <- rbind(c(1,2),
             c(1,2))
grid.arrange(datacentre_and_langugage_plot,
             rights_and_date_plot,
             # datacentre_plot,
             # allocator_plot,
             # creator_plot,
             # contributor_plot,
             # publisher_plot,
             # rights_plot,
             # language_plot,
             # date_plot,
             layout_matrix = lay)

# look at some relationships
datacentre_rights_table <- 
dc_arch %>% 
  mutate(the_text =  toupper(gsub(" |_|\\(|\\)", "-", rights)),
         the_text = gsub("(\\-)\\1+", "\\1", the_text),
         the_text = gsub("-$", "", the_text)) %>% 
  mutate(cc = case_when(
    grepl("SEMANTICS/OPENACCESS", the_text) ~ "EU Open Access",
    grepl("SEMANTICS/RESTRICTEDACCESS", the_text) ~ "EU Restricted Access",
    grepl("SEMANTICS/CLOSEDACCESS", the_text) ~ "EU Closed Access",
    grepl("CC-BY-[^NC-ND]|CC-BY$|ATTRIBUTION-LICENSE|ATTRIBUTION-[^NON]", the_text) ~ "CC-BY",
    grepl("CC-BY-NC-[^ND]|BY-NC-[^ND]|CC-NC$|ATTRIBUTION-NON-COMMERCIAL-", the_text) ~ "CC-BY-NC",
    grepl("CC-BY-NC-SA-[^ND]|CC-NC-SA$|ATTRIBUTION-NON-COMMERCIAL-SHARE", the_text) ~ "CC-BY-NC-SA",
    grepl("CC-BY-NC-ND|BY-NC-ND|ATTRIBUTION-NONCOMMERCIAL-NO-DERIVATIVE|ATTRIBUTION-NONCOMMERCIAL-NODERIVATIVES|ATTRIBUTION-NONCOMMERCIAL-NODERIVS|NAMENSNENNUNG-NICHTKOMMERZIELL-KEINEBEARBEITUNG|NAMENSNENNUNG-KEINE-KOMMERZIELLE-NUTZUNG", the_text) ~ "CC-BY-NC-ND",
    grepl("ADS|ARCHAEOLOGYDATASERVICE", the_text) ~ "ADS",
    grepl("CC0|CC-0|ZERO", the_text) ~ "CC-0"
  )) %>% 
  group_by(datacentre, cc) %>% 
  filter(!is.na(cc))  %>% 
  tally(sort = TRUE)

datacentre_rights_table[1:11,] %>% 
  ggplot(aes(cc, datacentre)) + 
  geom_point(aes(size = n),
             colour = "grey80") +
  theme_bw() + 
  xlab("") + 
  ylab("") +
  scale_size_continuous(range=c(5,25)) + 
  geom_text(aes(label = n))

# changes over time
library(ggrepel)

datacentre_by_year <- 
dc_arch %>% 
  group_by(yyyy_created, datacentre) %>% 
  tally(sort = TRUE) %>% 
  ungroup() %>% 
  filter(n > 150)

  ggplot(datacentre_by_year, 
         aes(yyyy_created,
             n,
             colour = datacentre)) +
  geom_line(size = 2) +
  theme_bw()  +
  scale_y_log10() +
  theme(legend.position = "none")  +
  facet_wrap(~ datacentre)

```
